---
title: "model"
author: "Jianhaoyan"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(dplyr)
library(ggplot2)
data_train<-read.csv("application_train.csv")
bureau<-read.csv("bureau.csv")
data_1<-inner_join(data_train,bureau,by="SK_ID_CURR")
##look at missing value
missing_data<-as.data.frame(sort(sapply(data_1, function(x)sum(is.na(x)))))
colnames(missing_data)[1]="count"
missing_data$features <- rownames(missing_data)
ggplot(missing_data)+
  geom_bar(mapping = aes(x=features,y=count),stat = "identity")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none") + ylab("Percentage of missingvalues") +
  xlab("Feature") + ggtitle("Understanding Missing Data")
dbraw<-missing_data%>%
  filter(count<300000)
column1<-as.matrix(dbraw$features)
data_raw<-as.data.frame(data_1[,column1])
```

#using brotua extracting features.
```{r}
#using brotua extracting features.
data_model_raw<-data_raw[,c("SK_ID_CURR","TARGET",
                            "CODE_GENDER","AMT_INCOME_TOTAL",
                            "AMT_CREDIT","AMT_ANNUITY.x",
                            "NAME_INCOME_TYPE","AMT_GOODS_PRICE",
                            "DAYS_EMPLOYED","EXT_SOURCE_3",
                            "EXT_SOURCE_2","OCCUPATION_TYPE",
                            "DAYS_REGISTRATION","DAYS_BIRTH",
                            "FLAG_OWN_CAR","FLAG_MOBIL","DAYS_ID_PUBLISH")]
#exit source is important, I choose to fill the missing data of ext_source
data_model_raw$EXT_SOURCE_2[is.na(data_model_raw$EXT_SOURCE_2)]<-"0"
data_model_raw$EXT_SOURCE_3[is.na(data_model_raw$EXT_SOURCE_3)]<-"0"
#
db_model_raw<-na.omit(data_model_raw)
db_model<-db_model_raw%>%
  group_by(OCCUPATION_TYPE)%>%
  summarise(average_income=mean(AMT_INCOME_TOTAL))
db_try<-left_join(db_model_raw,db_model,by="OCCUPATION_TYPE")
db_try<-db_try[,-4]
```




#looking at skewness
```{r}
library(ggplot2)
library(RPMG)
library(e1071)
library(DT)
library(data.table)
library(dplyr)
library(gridExtra)
doPlots <- function(data_in, fun, ii, ncol=3) {
  pp <- list()
  for (i in ii) {
    p <- fun(data_in=data_in, i=i)
    pp <- c(pp, list(p))
  }
  do.call("grid.arrange", c(pp, ncol=ncol))
}

plotHist <- function(data_in, i) {
  data <- data.frame(x=data_in[[i]])
  p <- ggplot(data=data, aes(x=x)) + geom_histogram(bins=100, fill="#0072B2", alpha = .9) + xlab(colnames(data_in)[i]) + theme_light() + 
    theme(axis.text.x = element_text(angle = 90, hjust =1))
  return (p)
}
#
doPlots(dt1_num, plotHist, ii = 1:11)
#
numeric_list <- unlist(lapply(db_try, is.numeric))
dt1_num <- setDT(db_try)[,..numeric_list]
skewValues <- as.data.frame(apply(dt1_num, 2, function(x) skewness(x, na.rm = TRUE)))
colnames(skewValues)[1] <- "skew_values"
#skewValues <- index_to_col(skewValues,'Column')
skewValues <- setDT(skewValues)[order (skew_values, decreasing = TRUE)]
skewValues[sample(1:nrow(skewValues), size = nrow(skewValues)),] %>% 
  datatable(filter = 'top', options = list(
    pageLength = 15, autoWidth = F
  ))
##We can find that "AMT_ANNUITY.x","AMT_GOODS_PRICE","DAYS_REGISTRACTION" have serious skwness problems, so we need to transform them.


```

##model
#AMT_CREDIT
```{r}
hist(db_try$AMT_CREDIT)
#It has lots of skewness.
db_try$AMT_CREDIT<-log(db_try$AMT_CREDIT)
hist(db_try$AMT_CREDIT)
#It seems to become much better than before.
#outlier
boxplot(db_try$AMT_CREDIT)
#remove outlier
x <- db_try$AMT_CREDIT
qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
caps <- quantile(x, probs=c(.05, .95), na.rm = T)
H <- 1.5 * IQR(x, na.rm = T)
print(qnt)
print(caps)
print(H)
db_try$AMT_CREDIT[db_try$AMT_CREDIT < (qnt[1] - H)] <- caps[1]
db_try$AMT_CREDIT[db_try$AMT_CREDIT > (qnt[2] + H)] <- caps[2]
boxplot(db_try$AMT_CREDIT)
```
#AMT_ANNUITY.x
```{r}
hist(db_try$AMT_ANNUITY.x)
#It has serious skewness issue.
db_try$AMT_ANNUITY.x<-log(db_try$AMT_ANNUITY.x)
hist(db_try$AMT_ANNUITY.x)
#Outliers
boxplot(db_try$AMT_ANNUITY.x)
x <- db_try$AMT_ANNUITY.x
qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
caps <- quantile(x, probs=c(.05, .95), na.rm = T)
H <- 1.5 * IQR(x, na.rm = T)
print(qnt)
print(caps)
print(H)
db_try$AMT_ANNUITY.x[db_try$AMT_ANNUITY.x < (qnt[1] - H)] <- caps[1]
db_try$AMT_ANNUITY.x[db_try$AMT_ANNUITY.x > (qnt[2] + H)] <- caps[2]
boxplot(db_try$AMT_ANNUITY.x)
```
#AMT_GOODS_PRICE
```{r}
#Skewness
hist(db_try$AMT_GOODS_PRICE)
#It has serious skewness problem.
db_try$AMT_GOODS_PRICE<-log(db_try$AMT_GOODS_PRICE)
hist(db_try$AMT_GOODS_PRICE)
#Outlier
boxplot(db_try$AMT_GOODS_PRICE)
x <- db_try$AMT_GOODS_PRICE
qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
caps <- quantile(x, probs=c(.05, .95), na.rm = T)
H <- 1.5 * IQR(x, na.rm = T)
print(qnt)
print(caps)
print(H)
db_try$AMT_GOODS_PRICE[db_try$AMT_GOODS_PRICE < (qnt[1] - H)] <- caps[1]
db_try$AMT_GOODS_PRICE[db_try$AMT_GOODS_PRICE > (qnt[2] + H)] <- caps[2]
boxplot(db_try$AMT_GOODS_PRICE)
```

#Days_Employed
```{r}
db_try$DAYS_EMPLOYED<-abs(db_try$DAYS_EMPLOYED)
#Skewness
db_try$DAYS_EMPLOYED<-log(db_try$DAYS_EMPLOYED)
hist(db_try$DAYS_EMPLOYED)
#Outliers
boxplot(db_try$DAYS_EMPLOYED)
x <- db_try$DAYS_EMPLOYED
qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
caps <- quantile(x, probs=c(.05, .95), na.rm = T)
H <- 1.5 * IQR(x, na.rm = T)
print(qnt)
print(caps)
print(H)
db_try$DAYS_EMPLOYED[db_try$DAYS_EMPLOYED < (qnt[1] - H)] <- caps[1]
db_try$DAYS_EMPLOYED[db_try$DAYS_EMPLOYED > (qnt[2] + H)] <- caps[2]
boxplot(db_try$DAYS_EMPLOYED)
```

#DAYS_REGESTION

```{r}
db_try$DAYS_REGISTRATION<-abs(db_try$DAYS_REGISTRATION)
#Skewness
hist(db_try$DAYS_REGISTRATION)
#Outliers
boxplot(db_try$DAYS_REGISTRATION)
x <- db_try$DAYS_REGISTRATION
qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
caps <- quantile(x, probs=c(.05, .95), na.rm = T)
H <- 1.5 * IQR(x, na.rm = T)
print(qnt)
print(caps)
print(H)
db_try$DAYS_REGISTRATION[db_try$DAYS_REGISTRATION < (qnt[1] - H)] <- caps[1]
db_try$DAYS_REGISTRATION[db_try$DAYS_REGISTRATION > (qnt[2] + H)] <- caps[2]
boxplot(db_try$DAYS_REGISTRATION)
```

#DAYS_BIRTH
```{r}
db_try$DAYS_BIRTH<-abs(db_try$DAYS_BIRTH)
#Skewness
hist(db_try$DAYS_REGISTRATION)
#Outliers
boxplot(db_try$DAYS_BIRTH)
x <- db_try$DAYS_BIRTH
qnt <- quantile(x, probs=c(.25, .75), na.rm = T)
caps <- quantile(x, probs=c(.05, .95), na.rm = T)
H <- 1.5 * IQR(x, na.rm = T)
print(qnt)
print(caps)
print(H)
db_try$DAYS_BIRTH[db_try$DAYS_BIRTH < (qnt[1] - H)] <- caps[1]
db_try$DAYS_BIRTH[db_try$DAYS_BIRTH > (qnt[2] + H)] <- caps[2]
boxplot(db_try$DAYS_BIRTH)
```



```{r}
db_try$TARGET<-as.factor(db_try$TARGET)
db_try$EXT_SOURCE_3<as.numeric(db_try$EXT_SOURCE_3)
db_try$EXT_SOURCE_2<-as.numeric(db_try$EXT_SOURCE_2)
db_test$TARGET<-as.factor(db_try$TARGET)
#sample
library(sampling)
library(caret)
trainIndex <- createDataPartition(db_try$OCCUPATION_TYPE, p = .5, list = FALSE, times = 1)
db_train <- db_try[ trainIndex,]
db_test<-db_try[-trainIndex]
#



#fill blank
library(lme4)
m1<-glmer(factor(TARGET)~factor(CODE_GENDER)+AMT_CREDIT+AMT_GOODS_PRICE+
            average_income+factor(FLAG_OWN_CAR)+DAYS_BIRTH+
            DAYS_EMPLOYED+EXT_SOURCE_2+
            (1|OCCUPATION_TYPE),
          data = db_train,family=binomial("logit"))
summary(m1)

vcov(m1) 
#
db_test$OCCUPATION_TYPE<-as.factor(db_test$OCCUPATION_TYPE)
m3.predict <- predict(m1, db_test,type="response")
m3.predict <- ifelse(m3.predict > 0.5,1,0)
head(m3.predict)
m3.predict <- as.factor(m3.predict)
compare <- data.frame(obs = db_test$TARGET, pred = m3.predict)
confusionMatrix(m3.predict, db_test$TARGET)
```
###Some thoughts.
My intial multilevel logistic regression model fits really bad. The accuracy of this model tells me that this model is just messy. I want to predict the probability of people that can not pay back money on time. But my model almost classifies all of clients as people pay back money on time.
I think the reason is that my data is seriously biased because my reposinve variable "TARGET" only has 8% of 1. So maybe I need to try another model. So can you give me some advice? Thank you professor.
#:) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) :) 


