---
title: "678 midterm project"
author: "Jianhaoyan"
date: "11/12/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Input Data and library packages
```{r}
data_train<-read.csv("application_train.csv")
bureau<-read.csv("bureau.csv")
bureau_balance<-read.csv("bureau_balance.csv")
previous_data<-read.csv("previous_application.csv")
creditcard_balance<-read.csv("credit_card_balance.csv")
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, skimr, GGally, plotly, viridis, 
               caret, DT, data.table)
library(dplyr)

```


#Introduction

In this project, I am asked to predict the TARGET variable (Clients’ repayment abilities) There are a number of datasets which are provided but for the purpose of simplicity the application dataset will be used.
The data is provided by the company called Home Credit, and they want to 

##EDA Part

In this part, we will use EDA to have an overview of our data.

#Target

The variables "Target" represents whether the clients have difficulties to reimburse the credits. 
"0" means that clents can reimburse on time while "1" means that clients have difficulties to reimburese.
```{r}
TotalNoofRows = nrow(data_train)

data_train %>%
  group_by(TARGET) %>%
  summarise(Count = n()/TotalNoofRows*100) %>%
  arrange(desc(Count)) %>%
  ungroup() %>%
  mutate(TARGET = reorder(TARGET,Count)) %>%
  
  ggplot(aes(x = TARGET,y = Count)) +
  geom_bar(stat='identity') +
  geom_text(aes(x = TARGET, y = 1, label = paste0("( ",round(Count,2)," %)",sep="")),
            hjust=0, vjust=.5, size = 4, colour = 'white',
            fontface = 'bold') +
  labs(x = 'TARGET', 
       y = 'Percentage', 
       title = 'TARGET distribution') +
  coord_flip() +
  theme_bw()
  
```

#AMI_CREDIT

This variable represents hoe much money the clients have borrowed.
```{r}
summary(data_train$AMT_CREDIT)
ggplot(data = data_train)+
  geom_histogram(aes(x=AMT_CREDIT))+
  labs(x= 'AMT_CREDIT',y = 'Count', title = paste('Distribution of', 'AMT_CREDIT')) 

  
```

#AMT_Total

This variable represents how much income each application earend per year.
```{r}
data_train%>%
  filter(AMT_INCOME_TOTAL<200000)%>%
  ggplot()+
  geom_histogram(aes(x=AMT_INCOME_TOTAL),bins = 20)+
  labs(aes(x='AMT-INCOME-TOTAL',y='Count',
           title='Distribution of AMT_INCOME_TOTAL'))+
  scale_x_continuous() +
  scale_y_continuous() +
  theme_bw()
```
#AMT_ANNUITY

This variable means how much money the clients need to repay per year.
```{r}
data_train%>%
  filter(AMT_ANNUITY< 100000)%>%
  ggplot(aes(x=AMT_ANNUITY))+
  geom_histogram(bins = 30)+
  labs(aes(x='AMT_ANNUITY',
           y='Count',
       title='Distribution of AMT_ANNUITY'))
```

#Name_Income_Type

This variable informs us whta kinds of jobs that clients do when they apply the credit.
```{r}
data_train%>%
  group_by(NAME_INCOME_TYPE,TARGET)%>%
  summarise(Count=n())%>%
  ggplot(aes(x=NAME_INCOME_TYPE,y=Count,fill=TARGET))+
  geom_bar(stat = 'identity',position = position_dodge(width = 1))+
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(aes(x='NAME_INCOME_TYPE',
           y='Count',
           title="Distributions of NAME_INCOME_TYPE"))
```
#Name_Occupation_Type
This variable tells us what the jobs of the clients do.
```{r}
data_train%>%
  group_by(TARGET,OCCUPATION_TYPE)%>%
  summarise(Count=n())%>%
  ungroup()%>%
  mutate(OCCUPATION_TYPE=reorder(OCCUPATION_TYPE,Count))%>%
  mutate(TARGET = as.factor(TARGET)) %>%
  ggplot(aes(x=OCCUPATION_TYPE,y=Count,fill=TARGET))+
  geom_bar(stat="identity",position = position_dodge(width = 1))+
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(aes(x='OCCUPATION_TYPE',
           y='Count',
           title='Distribution of Occupation'))
```

#Name_Education_Type

This variable illustrate the education level of clients
```{r}
data_train%>%
  filter(!is.na(NAME_EDUCATION_TYPE))%>%
  group_by(NAME_EDUCATION_TYPE,TARGET)%>%
  summarise(count=n())%>%
  ungroup()%>%
  mutate(NAME_EDUCATION_TYPE=reorder(NAME_EDUCATION_TYPE,count))%>%
  mutate(TARGET=factor(TARGET))%>%
  ggplot(aes(x=NAME_EDUCATION_TYPE,y=count,fill=TARGET))+
  geom_bar(stat="identity",position = position_dodge(width = 1))+
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(aes(x='Education_type',
           y='Count',
           title='Distribution of Education Level'))

```
#Name_Family_Status

This varibale mainly tells us that what's the family situation of client.
```{r}
data_pie1<-data_train%>%
  group_by(NAME_FAMILY_STATUS)%>%
  summarise(count=n())
pie(data_pie1$count,labels = data_pie1$NAME_FAMILY_STATUS,radius = 0.8)
  
```
#
```{r}
graph <- list()

for (i in 1:21){

    graph[[i]] <- data_train[, sapply(data_train, is.numeric)] %>% 
      na.omit() %>%
        select(TARGET,((i-1)*5+1):((i-1)*5+5)) %>%
        mutate(TARGET = factor(TARGET)) %>%
        ggpairs(aes(col = TARGET, alpha=.4))
    
    print(graph[[i]])
}
```
#We should join tables 
```{r}

data_1<-left_join(data_train,bureau,by="SK_ID_CURR")
living_status<-data_1[,45:91]%>%
  mutate(data_1$SK_ID_CURR)
##Then I want to cluster the housing condition. However, beacuse our data is so big, so we should randomly select 1000000 data.
db_try1<-sample(db_try$SK_ID_CURR,1000000)
db_try1<-data.frame(db_try1)
names(db_try1)[names(db_try1)=="living_status1"]="SK_ID_CURR"
db_try1$SK_ID_CURR<-factor(db_try1$SK_ID_CURR)
db_try1$SK_ID_CURR<-factor(db_try1$SK_ID_CURR)
db_samplesample<-
  dplyr::inner_join(db_try,db_try1,by="SK_ID_CURR") 
```
##Cluster

```{r}
setwd("/user4/mssphw1/ryanyan/Midtermroject")
```


```{r}
#library(Boruta)
#library(mlbench)
#library(dimRed)
#library(caret)
##Load dataset
#data_all[is.na(data_all)] <- 0

##prepare traing scheme
#control<-trainControl(method = "repeatedcv",number=10,repeats = 3)
##rain the model
#model<-train(TARGET~.,data = data_all,method="lvq",
             #preProcess="scale",trControl=control)
##estimate importance
#importance <- varImp(model, scale=FALSE)
##summarsie importance

```




##Because my dataset is too big, I choose to randomly select 
```{r}
save(train,file="data_train.RData")


```

##model fit

#merge table
```{r}
library(ggplot2)
library(dplyr)
data_raw<-inner_join(data_1,bureau_balance,by="SK_ID_BUREAU")
##look at all of the missing value
missing_data<-as.data.frame(sort(sapply(data_raw, function(x)sum(is.na(x)))))
colnames(missing_data)[1]="variable"
colnames(missing_data)[2]="count"


ggplot(missing_data)+
  geom_bar(mapping = aes(x=features,y=count),stat = "identity")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none") + ylab("Percentage of missingvalues") +
  xlab("Feature") + ggtitle("Understanding Missing Data")
##we can find their are some variables having tons of missing data, so 
column<-c()
dbraw<-missing_data%>%
  filter(count<300000)
column<-as.data.frame(dbraw$features)
data_raw<-as.data.frame(data_raw)
  
dim(column)
dim(data_raw)
##dealing with skewness
data_raw<-na.omit(data.raw)
```

